Spin canonical divisors of log stacky curves

### 2015-06-25 stacky_write_up/spin_cring.tex

\newcommand \subhalf[1]{\frac{{#1} - 1}{2{#1}}}
\newcommand{\se}[1]{\section*{Problem #1}}
\newcommand \halfcan{L}
\newcommand \Supp{\text{Supp}}
\newcommand \initial{\text{in}}
\newcommand \gin{\text{gin}}

@@

\section{Background}
\label{sec:background}
\todo{Reference independence of base field}
Look at Spencer-Kodaira \cite{kodaira:complex-manifolds}.
Include the following:
\begin{enumerate}
	\item Note that this result is independence of base field
	\item background on Gr\"{o}bner bases
	\item Notation $h^0 = \dim H^0$.
	\item Why we have these fractions $\frac{e_i - 1}{2e_i}$ and why $e_i$ must be odd.
\end{enumerate}

@@

\subsection{Definitions}
Here are some definitions.

\begin{defn}
\label{defn:sat}
\textbf{Saturations} of the canonical divisor, as defined in Voight
and Zureick-Brown ~\cite[Section 7.2]{vzb:stacky}.
\end{defn}

@@

\begin{lem}
\label{lem:sat-three-induction-g-0}
\todo{Make explicit assumptions on genus.}
Suppose $L'$ is a log half-canonical divisor of $\sx$ with course
space $X$ of genus 0 such that $'sat(Eff(\halfcan')) = 3$ with $R_
{\halfcan'} = k[x_3, x_4 , x_5, \ldots, x_m]/I'$. Let $L = L' + \frac
{1}{3}P$. Suppose $\deg x_i = i$ for $i \in \{3, 4, 5\}$ and that
the ordering on $k[x]$ satisfies
\begin{align*}
	\ord_{x_3}(f) < \ord_{x_3}(h) \implies f \prec h.
\end{align*}

@@

%$'sat(Eff(\halfcan))= 1$ and $'sat(Eff(\halfcan'))=2$. Further suppose $R_{\halfcan'} = k[x_2, 

@@

%Suppose $'sat(Eff(\halfcan))= 1$ and $'sat(Eff(\halfcan'))=2$. Further suppose 

@@

If $r > 5$, then we can use Lemma
~\ref{lem:sat-three-induction-g-0} to add ramified points with
stabilizer order $3$ to case (k) of Lemma
~\ref{lem:g_0_admissible_cases}, which corresponds to $\sigma_{11}
= (0; 3, 3, 3, 3, 3; 0), J_{11} = \{1, 2, 3, 4, 5\}$. This case
clearly satisfies the conditions of Lemma
~\ref{lem:sat-three-induction-g-0} (recall from Subsection ~\ref
{ssec:g_0_saturation} that $sat(Eff(\sigma_{11})) = 3$), and the
immediate consequence of parts (a) and (c) of Lemma
~\ref{lem:sat-three-induction-g-0} is that any $R(\sx', \Delta,
\halfcan')$ corresponding to signatures $\sigma'$ with ramification
orders all equal to $3$ for any $r > 5$ is generated up to
degree $e := \max(5, e_1', \ldots, e_r')$ with relations generated
up to degree $2e$. Furthermore, these cases satisfy all of the
conditions of Theorem ~\ref{thm:ram_order_ind}.

>>>>

\newcommand \subhalf[1]{\frac{{#1} - 1}{2{#1}}}
\newcommand{\se}[1]{\section*{Problem #1}}
\newcommand \halfcan{L}
\newcommand \Supp{\text{Supp}}
\newcommand \initial{\text{in}}
\newcommand \gin{\text{gin}}
\newcommand \Eff{\text{Eff}}
\newcommand \sat{\text{sat}}

@@

\section{Background}
\label{sec:background}
Look at Spencer-Kodaira \cite{kodaira:complex-manifolds}.
Include the following:
\begin{enumerate}
	\item Note that this result is independence of base field
	\item background on Gr\"{o}bner bases
	\item Notation $h^0 = \dim H^0$.
	\item Why we have these fractions $\frac{e_i - 1}{2e_i}$ and why $e_i$ must be odd.
\end{enumerate}

@@

\subsection{Definitions}
We reserve the notation $\halfcan$ for the halfcanonical divisor
where $\halfcan \sim $.

Here are some definitions.

We define the notion of the saturation of a divisor, taken from
Voight and Zureick-Brown ~\cite[Section 7.2]{vzb:stacky}.

\begin{defn}
Let $D$ be a divisor on $\sx$. The \textbf{effective monoid} of $D$
is the monoid
\[
	\Eff(D) = \{d \in \BZ_{\geq 0} : \deg \lfloor dD \rfloor \geq 0 \}
\]
\end{defn}

\begin{defn}
\label{defn:sat}
The \textbf{saturation} for a monoid $M \subseteq \BZ_{\geq 0}$,
denoted $\sat(M)$, is the smallest integer $s$ such that $M
\supseteq \BZ_{\geq s}$, if such an integer exists.
\end{defn}

\begin{rem}
For our purposes, it is useful to call the saturation of the
effective monoid of a divisor $D$ as the saturation $s$ of the
divisor $D$ on $\sx$. In this case, the saturation $s$ of a divisor
$D$ on $\sx$ (i.e. $\sat(\Eff(D))$) is the smallest positive $s \in
\BZ$ such that $\deg \lfloor dD \rfloor \geq 0$ for all $d \geq s$.
\end{rem}

@@

\begin{lem}
\label{lem:sat-three-induction-g-0}
\todo{Make explicit assumptions on genus.}
Suppose $L'$ is a log half-canonical divisor of $\sx$ with course
space $X$ of genus 0 such that $\sat(\Eff(\halfcan')) = 3$ with $R_
{\halfcan'} = k[x_3, x_4 , x_5, \ldots, x_m]/I'$. Let $L = L' + \frac
{1}{3}P$. Suppose $\deg x_i = i$ for $i \in \{3, 4, 5\}$ and that
the ordering on $k[x]$ satisfies
\begin{align*}
	\ord_{x_3}(f) < \ord_{x_3}(h) \implies f \prec h.
\end{align*}

@@

%$\sat(\Eff(\halfcan))= 1$ and $\sat(\Eff(\halfcan'))=2$. Further suppose $R_{\halfcan'} = k[x_2, 

@@

%Suppose $'\sat(\Eff(\halfcan))= 1$ and $'\sat(\Eff(\halfcan'))=2$. Further suppose 

@@

If $r > 5$, then we can use Lemma
~\ref{lem:sat-three-induction-g-0} to add ramified points with
stabilizer order $3$ to case (k) of Lemma
~\ref{lem:g_0_admissible_cases}, which corresponds to $\sigma_{11}
= (0; 3, 3, 3, 3, 3; 0), J_{11} = \{1, 2, 3, 4, 5\}$. This case
clearly satisfies the conditions of Lemma
~\ref{lem:sat-three-induction-g-0} (recall from Subsection ~\ref
{ssec:g_0_saturation} that $\sat(\Eff(\sigma_{11})) = 3$), and the
immediate consequence of parts (a) and (c) of Lemma
~\ref{lem:sat-three-induction-g-0} is that any $R(\sx', \Delta,
\halfcan')$ corresponding to signatures $\sigma'$ with ramification
orders all equal to $3$ for any $r > 5$ is generated up to
degree $e := \max(5, e_1', \ldots, e_r')$ with relations generated
up to degree $2e$. Furthermore, these cases satisfy all of the
conditions of Theorem ~\ref{thm:ram_order_ind}.
